The contact value approximation for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-06-13 papers/pair-correlation/paper.tex
divy up writing tasks and work on fit Tested on bennet. Took 0:30.70.

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\refnote}{\red{[ref]}}

@@

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\green{Jeff:} \emph{#1}]}}
\newcommand{\pahosays}[1]{{\color{red} [\green{Paho:} \emph{#1}]}}

@@

\fixme{replace approximation with approach}

@@

\fixme{Somewhere above introduce the question of whether g2 is
  expressed in terms of V or n}

@@

\fixme{introduce this as methods given V}

@@

\fixme{introduce this as methods given n}

@@

Sokolowski and Fischer addressed the shortcomings of the theory of
Fischer and Methfessel by modifying this approach to use
averages, centered on the two points $\rr_1$ and $\rr_2$:
\begin{align}
  g^{(2)}(\rr_1,\rr_2) \approx g\left(r_{12},
  \tfrac12(\bar{n}(\rr_1)+\bar{n}(\rr_2))\right)
  \label{eq:sokolowski}
\end{align}
where their averaged density $\bar{n}(\rr)$ is given by:
\begin{align}
  \bar{n}(\rr) \equiv \frac{3}{4\pi (0.8\sigma)^3}\int n(\rr')\Theta(0.8\sigma - |\rr-\rr'|) d\rr'
\end{align}
is the density averaged over a sphere with diameter
$0.8\sigma$~\cite{sokolowski1992role}.  The value 0.8 in this formula
was arrived at by fitting to Monte Carlo simulation.  Although
Eq.~\ref{eq:sokolowski} has the advantages of only involving density
averages at the points at which the pair distribution function is
desired, it cannot be written as a single-site convolution, since the
convolution kernel depends on both points.  However, this approach has
been used by two papers to do
\fixme{what?}~\cite{wadewitz2000application, winkelmann2001liquid}.

@@

\davidsays{Please edit!}\fixme{Note that the HS free energy is used
  for two purposes when applying Eq.~\ref{eq:gsigma-exact} : it is
  minimized (together with an external potential) to find the density
  $n(\rr)$.  Then its functional derivative is used to find
  $g_\sigma(\rr)$.  In application of perturbation theory, the HS
  functional would only be used alone for the latter purpose, as the
  density would be determined by the total free energy, which
  incorporates both the HS free energy and a perturabative
  contribution.}

@@

\fixme{Explain why the separable version is efficient.}

>>>>

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}
\newcommand{\blue}[1]{{\bf \color{blue} #1}}
\newcommand{\cyan}[1]{{\bf \color{cyan} #1}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\refnote}{\red{[ref]}}

@@

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\cyan{Jeff:} \emph{#1}]}}
\newcommand{\pahosays}[1]{{\color{red} [\blue{Paho:} \emph{#1}]}}

@@

\fixme{replace approximation with approach}\jeffsays{I'm stuck with this.}

@@

\fixme{Somewhere above introduce the question of whether g2 is
  expressed in terms of V or n}\davidsays{I'll take a stab at this}

@@

\fixme{introduce this as methods given V}\davidsays{I'll take a stab
  at this}

@@

\fixme{introduce this as methods given n}\davidsays{I'll do this}

@@

Sokolowski and Fischer addressed the shortcomings of the theory of
Fischer and Methfessel by modifying this approach to use
averages, centered on the two points $\rr_1$ and $\rr_2$:
\begin{align}
  g^{(2)}(\rr_1,\rr_2) \approx g\left(r_{12},
  \tfrac12(\bar{n}(\rr_1)+\bar{n}(\rr_2))\right)
  \label{eq:sokolowski}
\end{align}
where their averaged density $\bar{n}(\rr)$ is given by:
\begin{align}
  \bar{n}(\rr) \equiv \frac{3}{4\pi (0.8\sigma)^3}\int n(\rr')\Theta(0.8\sigma - |\rr-\rr'|) d\rr'
\end{align}
is the density averaged over a sphere with diameter
$0.8\sigma$~\cite{sokolowski1992role}.  The value 0.8 in this formula
was arrived at by fitting to Monte Carlo simulation.  Although
Eq.~\ref{eq:sokolowski} has the advantages of only involving density
averages at the points at which the pair distribution function is
desired, it cannot be written as a single-site convolution, since the
convolution kernel depends on both points.  However, this approach has
been used by two papers to construct classical density functionals for
studying the liquid vapor interface~\cite{wadewitz2000application,
  winkelmann2001liquid}.

@@

\davidsays{Please edit!}\jeffsays{I will!}\fixme{Note that the HS free energy is used
  for two purposes when applying Eq.~\ref{eq:gsigma-exact} : it is
  minimized (together with an external potential) to find the density
  $n(\rr)$.  Then its functional derivative is used to find
  $g_\sigma(\rr)$.  In application of perturbation theory, the HS
  functional would only be used alone for the latter purpose, as the
  density would be determined by the total free energy, which
  incorporates both the HS free energy and a perturabative
  contribution.}

@@

\fixme{Explain why the separable version is efficient.}\davidsays{I'll
  do it.}
